Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-29 manuscript/manuscript.Rmd
a sentence

Reinforcement learning, on the other hand, can provide a model-free approach to control theory.\footnote{There are approaches to perform model-based reinforcement learning. While we will not focus on these in this paper they are discussed in \cite{tbd1, tbd2}.}
While a model is often used to generate training data, this model is not directly used by model-free RL algorithms.
This provides more flexibility to use RL in instances where the model of the system is not accurately known.
In fact, it has been shown that model-free RL outperforms model-based alternatives in such instances \cite{Janner et al., 2019}.

@@

Finally, in our study case, we have shown that the ‘‘rest periods’’ so prominent in both the DRL solution and in the optimal bang-bang policy -- periods of several time steps with no fishing at all -- may be important to maintain the sustainability of the fishery and to increase its long-term profits.
This hypothesis could be explored in more generality as it might apply to a wide variety of models with different optimal control strategies.

>>>>

Reinforcement learning, on the other hand, can provide a model-free approach to control theory.\footnote{There are approaches to perform model-based reinforcement learning. While we will not focus on these in this paper they are discussed in \cite{tbd1, tbd2}.}
While a model is often used to generate training data, this model is not directly used by model-free RL algorithms.
This provides more flexibility to use RL in instances where the model of the system is not accurately known.
In fact, it has been shown that model-free RL outperforms model-based alternatives in such instances \cite{mbpo}.

@@

Finally, in our study case, we have shown that the ‘‘rest periods’’ -- periods of several time steps with no fishing at all -- prominent in both the DRL solution and in the optimal bang-bang policy, may be important to maintain the sustainability of the fishery and to increase its long-term profits.
This hypothesis could be explored in more generality as it might apply to a wide variety of models.
